---
title: "GW Assignment - Biden Transition"
author: "YOUR NAME HERE"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(janitor)
library(scales)
library(gt)
library(kableExtra)
options(dplyr.summarise.inform = FALSE)

#run the script for step 03 to update the datasets to capture the current live verions
#note that this will also run step 01 and step 02, since the step 03 file "sources" both of those scripts
#and load all the new dataset objects into the environment (you'll see them populate on the upper right window)

source("03_compare_current_with_previous_WITHSOLUTIONS.R") #note that here we source the SOLUTIONS version


```

**Note: use either kable/kableExtra or gt tables to format your final tables for the questions below. You'll likely find it easier to figure out the data parts first, then once that's done add the table formatting.**

###
# AGENCY TEAMS

Come up with the necessary R code to return the following for the agency review teams.

### *New Names*

Below write code to show the new names added to the agency review team lists since the prior data provided.  
  

```{r, echo=FALSE}

newnames %>% 
  select(agency, name, most_recent_employment, on_multiple_teams, team_lead) %>% 
  gt() %>%
  tab_header(
    title = "New transition agency review team names"
  ) %>%
  tab_options(table.align = "left") %>%
  cols_align(
    align = "center",
    columns = vars(team_lead, on_multiple_teams)
  ) 

 

```

###
### *Aggregate Team Changes*

Add data to show the total number of people appointed to each agency team, along with change since last time reflecting the number of new people added. Omit agencies with no change at all.  
  

```{r, echo=FALSE}

agencycount_compare %>% 
  filter(change != 0) %>% 
  gt() %>%
  tab_options(table.align = "left") %>% 
 tab_style(
    style = list(
      cell_text(weight = "bold",
                color = "darkgreen")
      ),
    locations = cells_body(
      columns = vars(change)
      )
  ) 


```

###
### *Largest and Smallest Overall*

###
Show the top 10 **largest** agency review teams as of today:

```{r, echo=FALSE}

agencycount_compare %>% 
  select(agency, current) %>% 
  arrange(desc(current)) %>% 
  head(10) %>% 
  gt() %>%
  tab_options(table.align = "left") 




```

###
Show the top **smallest** agency review teams as of today - which we'll define here as less than five members:

```{r, echo=FALSE}

agencycount_compare %>% 
  select(agency, current) %>% 
  arrange(current) %>% 
  filter(current < 5) %>% 
  gt() %>%
  tab_options(table.align = "left") 



```


#
# WHITE HOUSE SENIOR STAFF

Come up with the necessary R code to return the following for the WH senior staff.

### *New Names*

Below write code to show the new names added to the senior staff lists since the prior data provided.  
  

```{r, echo=FALSE}

newnames_staff %>% 
  select(name, title) %>% 
  gt() %>%
  tab_header(
    title = "New WH senior staff names"
  ) %>%
  tab_options(table.align = "left") 

 

```

###
### *Total Number of Current vs. Previous*

Add code to show the total number of people currently named to the WH senior staff, vs. the previous total number.  
  

```{r, echo=FALSE}

#find current number of rows (e.g. people)
num_staffcurrent <- staff_data_current %>% 
  nrow()

#find previous number of people
num_staffprevious <- staff_data_previous %>% 
  nrow()

#calculate the difference
num_staffdiff <- num_staffcurrent - num_staffprevious

#turn into a dataframe
df_staff <- data.frame("current_total" = num_staffcurrent, 
                   "previous_total" = num_staffprevious,
                   "difference" = num_staffdiff)

df_staff %>% 
  gt()

```

Another option could be to use RMarkdown's "inline" code option to write it out as a sentence. Like this:  
  
There are currently a total of `r num_staffcurrent` White House senior staffers named on the website, up from `r num_staffprevious` last time, for a difference of `r num_staffdiff` new people added. 
  
  
Or with some bolded sections:

There are **currently a total of `r num_staffcurrent`** White House senior staffers named on the website, **up from `r num_staffprevious`** last time we checked, for a difference of **`r num_staffdiff` new people** added. 
